---
title: "Q10: Covid19"
author: "Alma Renero"
PID: A15718243
format: pdf
editor: visual
---

## COVID Graph

#First I downloaed the cvs file from the website provided.Then I read the file on R and assign it a new name 'covid19'

```{r}
covid19 <- read.csv("covid19_variants.csv")
```

```{r}
head(covid19)
```

# Download the R packages: 'lubridate' and 'dplyr'. Making sure to write library to be able to use these packages

```{r}
library(lubridate)
library(dplyr)
library(ggplot2)
```

#Labeled the columns on the cvs 'covid19' file. Labeled this to have on the information I need for my graph.

```{r}
date = covid19[1]
test_date = date[1:8980,]
date_obj = as.Date(test_date)
variant = covid19[4]
percentage = covid19[6]

```

#usingthe above labels,I made a new data frame with the information I need.

```{r}
df <- data.frame(date = date_obj, values = percentage, variants = variant)
head(df)
```

#Using the lubridate I want to switch the date to show only the month and the year.

```{r}
df2 <- df %>%
  group_by(month = lubridate::floor_date(date, "month"),variant_name) %>%summarize(summary_variable = mean(percentage))
```

# Created more data frame

```{r}
df3 <- df[- grep("Other", df$variant_name),]
```

```{r}
df4 <- df3[- grep("Total", df2$variant_name),]
df4
```

# Using ggplot I made the graph looking at the percent specimen versus the date

```{r}
percentage_plot <- ggplot(df3,aes(x = date, y = percentage))

percentage_plot + geom_line(aes(color = variant_name)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) + scale_x_date(date_breaks = "1 month",date_labels = "%b-%Y") +
  labs(x= "Date", y= "Specimen Percentage")
```
